Improving Software Maintainability through Automated Refactoring of Code Clones

### 2020-01-09 ecoop/paper.tex
Updates from Overleaf

\begin{figure*}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
package com.sb.game;

@@

	public void addTen(int x) {
|\highlightYellow|		x = x + 10; // Addition
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
package com.sb.fruitgame;

@@

	public void concatTen(String x) {
|\highlightYellow|		x = x + 10; // String concat
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\caption{Example of textually equal code fragments that differ in functionality.}
\label{fig:type1}
\end{figure*}

@@

\begin{figure*}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|int a = getA();
|\highlightYellow|while(a<1000) {
|\highlightYellow|  a *= 5;
  doC();
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
|\highlightYellow|int a = getA();
|\highlightYellow|while(a<1000) {
|\highlightYellow|  a *= 5;
  doB(a);
}
\end{javacode}}
\end{parcolumns}
\caption{A clone that spans a block partially.}
\label{fig:refactorabilitypartialblock}
\end{figure*}

@@

\begin{table*}
\centering
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}%
%}
\caption{Influence on maintainability of refactoring clones with the specified relation categories.}
\label{tab:relation_refactor}
\end{table*}

@@

\begin{figure*}
  \includegraphics[width=1\textwidth]{img/tokenvolume}
  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability.}
  \label{fig:maintainabilityscore}
\end{figure*}

@@

\begin{table*}
\centering
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
\rowcolor[HTML]{FFCCC9}
Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}
\caption{Average metric values for refactorings of clone classes with the specified return category}
\label{tab:return}
\end{table*}

>>>>

%\begin{figure}
% \begin{parcolumns}{2}
% \colchunk[1]{
\begin{lstlisting}[language=Java,escapechar=|,label=list:8-6,captionpos=t,float,abovecaptionskip=-\medskipamount,tabsize=2, basicstyle=\small, linewidth=6cm]
package com.sb.game;

@@

	public void addTen(int x) {
|\highlightYellow|		x = x + 10; // Addition
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{lstlisting}% }
%\colchunk[2]{
\begin{lstlisting}[language=Java,escapechar=|,label=list:8-6,captionpos=t,float,abovecaptionskip=-\medskipamount,tabsize=2, basicstyle=\small, linewidth=6cm]
package com.sb.fruitgame;

@@

	public void concatTen(String x) {
|\highlightYellow|		x = x + 10; // String concat
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{lstlisting} %}
%\end{parcolumns}
%\caption{Example of textually equal code fragments that differ in functionality.}
%\label{fig:type1}
%\end{figure}

\begin{lstlisting}[caption={Useless code},label=list:8-6,captionpos=t,float,abovecaptionskip=-\medskipamount]
for i:=maxint to 0 do 
begin 
    j:=square(root(i));
end;
\end{lstlisting}

@@

\begin{figure}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|int a = getA();
|\highlightYellow|while(a<1000) {
|\highlightYellow|  a *= 5;
  doC();
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
|\highlightYellow|int a = getA();
|\highlightYellow|while(a<1000) {
|\highlightYellow|  a *= 5;
  doB(a);
}
\end{javacode}}
\end{parcolumns}
\caption{A clone that spans a block partially.}
\label{fig:refactorabilitypartialblock}
\end{figure}

@@

\begin{table}
\centering
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}%
%}
\caption{Influence on maintainability of refactoring clones with the specified relation categories.}
\label{tab:relation_refactor}
\end{table}

@@

\begin{figure}
  \includegraphics[width=1\textwidth]{img/tokenvolume}
  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability.}
  \label{fig:maintainabilityscore}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
\rowcolor[HTML]{FFCCC9}
Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}
\caption{Average metric values for refactorings of clone classes with the specified return category}
\label{tab:return}
\end{table}
